WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2014-05-24 ms.tex
Marginpar whitespace

The prevailing technique for detection of \acp{GW} from \acp{CBC} is to realize a \ac{MLE} from the likelihood in \Eref{eq:gaussian-likelihood} and the signal model in \Eref{eq:signal-model}. Concretely, this results in a bank of matched filters, or template waveforms that are convolved with the incoming data stream. The matched filter or \ac{ML} point estimates of the signal parameters are
%
\begin{eqnarray}
\hat{\boldsymbol\theta}_\mathrm{in}, \{\hat\tau_i\}_i &=& \argmax_{\boldsymbol\theta_\mathrm{in}, \{\hat\tau_i\}_i} \sum_i \frac{1}{{\sigma_i}^2} \left| \int_0^\infty \frac{h^*(\omega; \boldsymbol\theta_\mathrm{in}) x_i(\omega) e^{i \omega \tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right|^2 \\
\hat\rho_i &=& \frac{1}{\sigma_i} \left| \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right| \\
\hat\gamma_i &=& \arg \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega.
\end{eqnarray}
%
A detection candidate consists of the set $\{\hat{\boldsymbol\theta}_\mathrm{in}, \left\{ \hat\rho_i, \hat\gamma_i, \hat\tau_i \right\}_i\}$. There are various ways to characterize the significance of a
detection candidate, but in Gaussian noise the combined SNR $\hat\rho_\mathrm{c}$ suffices,
%
\marginpar{What is the least that I can get away with saying about false alarm rate estimation and likelihood ratios?}
%
\begin{equation}
	\hat\rho_\mathrm{c} = \sqrt{\sum_i {\hat\rho_i}^2}.
\end{equation}.

@@

We have no explicit prior on the intrinsic parameters; in our analysis they are fixed at their \ac{ML} estimates, $\hat{\boldsymbol\theta}$. The distance prior is given by a user-selected power of distance, ${D_\mathrm{L}}^m$, where $m=2$ for a prior that is uniform in volume, and $m=-1$ for a scale-invariant prior that is uniform in $\log D_\mathrm{L}$. The priors are bounded as follows:
%
\marginpar{Need to discuss $D_{\mathrm{L},\mathrm{min}}$, $D_{\mathrm{L},\mathrm{max}}$, and how they are selected automatically if the user does not provide them.}
%
\begin{eqnarray*}
	D_\mathrm{L} &\in& [D_{\mathrm{L},\mathrm{min}}, D_{\mathrm{L},\mathrm{max}}] \\
	t_\oplus &\in& [-\infty, \infty] \\
	u &\in& [0, 1] \\
	\psi &\in& [0, \pi/2)
\end{eqnarray*}
%
The prior does not permit negative values of $u$ because only even powers of $u$ appear in \Eref{eq:snr-model}. The prior only permits $\psi$ to run to $\pi/2$ because only trigonometric functions of $4\psi$ appear in \Eref{eq:snr-model}.

>>>>

The prevailing technique for detection of \acp{GW} from \acp{CBC} is to realize a \ac{MLE} from the likelihood in \Eref{eq:gaussian-likelihood} and the signal model in \Eref{eq:signal-model}. Concretely, this results in a bank of matched filters, or template waveforms that are convolved with the incoming data stream. The matched filter or \ac{ML} point estimates of the signal parameters are
%
\begin{eqnarray}
\hat{\boldsymbol\theta}_\mathrm{in}, \{\hat\tau_i\}_i &=& \argmax_{\boldsymbol\theta_\mathrm{in}, \{\hat\tau_i\}_i} \sum_i \frac{1}{{\sigma_i}^2} \left| \int_0^\infty \frac{h^*(\omega; \boldsymbol\theta_\mathrm{in}) x_i(\omega) e^{i \omega \tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right|^2 \\
\hat\rho_i &=& \frac{1}{\sigma_i} \left| \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega \right| \\
\hat\gamma_i &=& \arg \int_0^\infty \frac{h^*(\omega; \hat{\boldsymbol\theta}_\mathrm{in}) x_i(\omega) e^{i \omega \hat\tau_i}}{S_i(\omega)} \,\mathrm{d}\omega.
\end{eqnarray}
%
A detection candidate consists of the set $\{\hat{\boldsymbol\theta}_\mathrm{in}, \left\{ \hat\rho_i, \hat\gamma_i, \hat\tau_i \right\}_i\}$. There are various ways to characterize the significance of a
detection candidate, but in Gaussian noise the combined SNR $\hat\rho_\mathrm{c}$ suffices,
%
\marginpar{What is the least that I can get away with saying about false alarm rate estimation and likelihood ratios?}%
%
\begin{equation}
	\hat\rho_\mathrm{c} = \sqrt{\sum_i {\hat\rho_i}^2}.
\end{equation}.

@@

We have no explicit prior on the intrinsic parameters; in our analysis they are fixed at their \ac{ML} estimates, $\hat{\boldsymbol\theta}$. The distance prior is given by a user-selected power of distance, ${D_\mathrm{L}}^m$, where $m=2$ for a prior that is uniform in volume, and $m=-1$ for a scale-invariant prior that is uniform in $\log D_\mathrm{L}$. The priors are bounded as follows:
%
\marginpar{Need to discuss $D_{\mathrm{L},\mathrm{min}}$, $D_{\mathrm{L},\mathrm{max}}$, and how they are selected automatically if the user does not provide them.}%
%
\begin{eqnarray*}
	D_\mathrm{L} &\in& [D_{\mathrm{L},\mathrm{min}}, D_{\mathrm{L},\mathrm{max}}] \\
	t_\oplus &\in& [-\infty, \infty] \\
	u &\in& [0, 1] \\
	\psi &\in& [0, \pi/2)
\end{eqnarray*}
%
The prior does not permit negative values of $u$ because only even powers of $u$ appear in \Eref{eq:snr-model}. The prior only permits $\psi$ to run to $\pi/2$ because only trigonometric functions of $4\psi$ appear in \Eref{eq:snr-model}.
